Artistic Curve Steganography Carried by Musical Audio

### 2022-10-30 writeup/paper.tex
Adding Turk results

\subsection{Listening Experiment}

@@

>>>>

Below we assess the performance of our system on an extensive set of tests

Show caltech-101 and meshseg examples

\subsection{Quantitative Metrics}

\subsection{Subjective Listening Experiment}

\begin{figure}
  \centering
  \includegraphics[width=0.8\columnwidth]{Turk.pdf}
  \caption{Results of the listening experiment on the Amazon Mechanical Turk}
  \label{fig:TurkResults}
\end{figure}

@@

46 unique Turkers, 21 of whom participated in at least 40 rankings.

Figure~\ref{fig:TurkResults} shows the results.  Mean opinion scores are correlated with $\lambda$, but there's not much of a difference between $\lambda=0.1$ and $\lambda=1$, which suggests using the former as a rule of thumb due to its lower geometric distortion.
